### 2024-09-17 cognitive-bias.qmd
20240917 - risk aversion

Risk aversion is the tendency to prefer outcomes with low uncertainty (compared to outcomes with greater uncertainty).
For instance, a fantasy manager may prefer to draft players who have demonstrated performance compared to players right out of college with no proven history in the NFL.

>>>>

*Risk aversion bias* is the tendency to prefer outcomes with low uncertainty (i.e., risk), even if they offer lower potential rewards compared to outcomes with greater uncertainty but potentially greater rewards.
Risk aversion leads people to select safer options but may lead them to miss out on higher-gain opportunities.
For instance, risk aversion may lead a fantasy manager to start players who are more steady (i.e., show greater game-to-game [consistency](#sec-evalHistoricalConsistency)) over players who are more volatile (i.e., show greater game-to-game variability) but have higher upside potential.
